### 2008-12-06 doc/sec/Sec_paper.tex
related work and reference

\begin{center}
\includegraphics[width=3.6362in,height=3.3339in]{Secpaper-img1.png}
\end{center}
{\centering
Figure 1. The example of Host Environment Daemon deployed with A-REX and
File services
\par}

@@

3.6 Discussion

@@

There is some effort to add GSI support to adapt to the strict security
requirement including GSI from grid middlewares, such as GSI plug-in
for gSOAP[17]. The GSI MCC implemented in ARC can also achieve the same
functionality as gSOAP. Moreover, the ARC solution is flexible than the
gSOAP solution, because both the GSI MCC of service and client sides
are pluggable, which means service and client developer of ARC do not
need to modify the service or client implementation in order to add or
remove the GSI functionality.

Shibboleth

GridShib

gLite Delegation Service?

SWITCH SLCS Service

the CCGrid 06 paper: Shibboleth-Protected privilege management
infrastructure

Delegation service : gridsite

@@

\textstyleCitation{\textup{[8]Web Services Security(WS-Security).
www.oasis-open.org/committees/wss/}}

@@

\textstyleCitation{\textup{[12] Design document of new version ARC.
}}\url{https://www.knowarc.eu/documents/Knowarc_D1.1-1_07.pdf}

@@

\textstyleCitation{\textup{[17]}}\textstyleCitation{\textup{Giovanni
Aloisio, Massimo Cafaro, Italo Epicoco, Daniele Lezzi, and Robert van
Engelen, }}\textstyleCitation{The GSI plug-in for gSOAP: Enhanced
Security, Performance, and Reliability}\textstyleCitation{\textup{, in
the ITCC conference 2005, IEEE Press, Volume I, pages 304-309.}}

>>>>

\begin{center}
\includegraphics[width=3.7465in,height=3.3764in]{Secpaper-img1.png}
\end{center}

{\centering
Figure 1. The example of Host Environment Daemon deployed with A-REX and
File services
\par}

@@

@@

Similar work that integrates Shibboleth and Grid middleware does exist.
GridShib[17][18] uses Shibboleth to get entity{\textquotesingle}s
attribute for the authorization of services developed in Globus Tookit.
Unlike the work of this paper, GridShib does not use
Shibboleth{\textquotesingle}s native login handlers for authentication
to Shibboleth IdP, instead, a new login handler specific for X.509
based authentication is developed for Shibboleth IdP, and a credential
service is developed for acting as an online-CA, authenticating the
user, and issuing short-lived X.509 credential.

SWITCH short-lived credential service (SLCS) [19] provides a SLCS
service and client. The benefit of our work comparing to the
SWTCH{\textquotesingle}s solution is the SLCS service and client is
based on Web Service, so that it can be implemented in any Web Service
container while keeping interoperability.

In terms of delegation, apart from the credential delegation mechanism
from GSI [2][20], [21] proposes a delegation protocol based on the
WS-Trust [22] in order to provide a standard and interoperable protocol
for delegation in Grids. WS-Trust will also be adopted by ARC
middleware to express the specifications required to define delegation
protocol in a standard way. Gridsite implements a X.509 credential
delegation solution [23] based on Web Service, with which ARC
delegation client can easily interoperate.

GSI plug-in for gSOAP[24] adds GSI support for gSOAP Web Service tookit.
The GSI MCC implemented in ARC can also achieve the same functionality
as this plug-in. Moreover, the ARC solution is more flexible than it,
because GSI MCC of both service and client sides are pluggable, which
means service and client developer of ARC do not need to modify the
service or client implementation in order to add or replace the GSI
functionality.

@@

\textstyleCitation{\textup{[8]OASIS Web Services Security.
www.oasis-open.org/committees/wss/}}

@@

\textstyleCitation{\textup{[12]Design document of new version ARC.
}}\url{https://www.knowarc.eu/documents/Knowarc_D1.1-1_07.pdf}

@@

[17]V. Welch, T. Barton, K. Keahey and F. Siebenlist. Attributes,
Anonymity, and Access: Shibboleth and Globus Integration to Facilitate
Grid Collaboration. 4th Annual PKI R\&D Workshop, 2005.

[18]T. Barton, J. Basney, T. Freeman, T. Scavo, F. Siebenlist, V. Welch,
R. Ananthakrishnan, B. Baker, and K. Keahey. Identity Federation and
Attribute-based Authorization through the Globus Toolkit, Shibboleth,
Gridshib, and MyProxy. 5th Annual PKI R\&D Workshop, 2006.

[19]SWITCH Short Lived Credential Service.
\url{http://www.switch.ch/grid/slcs/}

[20]V. Welch, I. Foster, C. Kesselman, O. Mulmo, L. Pearlman, S. Teucke,
J. Gawor, S. Meder and F. Siebenlist. X.509 proxy certificate for
dynamic delegation, Proceeding of the 3rd Annual PKI R\&D Workshop,
2004.

[21]M. Ahsant, J. Basney, and O. Mulmo. Grid Delegation Protocol, UK
Workshop on Grid Security Experiences, Oxford. 2004.

[22]OASIS WS-Trust specification.
\url{http://docs.oasis-open.org/ws-sx/ws-trust/200512}

[23]gridsite elegation service.
http://www.gridsite.org/wiki/Delegation\_protocol

\textstyleCitation{\textup{[24]}}\textstyleCitation{\textup{Giovanni
Aloisio, Massimo Cafaro, Italo Epicoco, Daniele Lezzi, and Robert van
Engelen, The GSI plug-in for gSOAP: Enhanced Security, Performance, and
Reliability, in the ITCC conference 2005, IEEE Press, Volume I, pages
304-309.}}
